### 2018-08-06 paper/design.tex
Design: rejects on and accepts one of Adrien's changes

Our goal is to enable private and reliable file exchange between users 
participating in the system, by using their respective devices only.
When Alice and Bob, two users of our system, want to exchange a file \(f\) 
through \name, they start by sharing some information out-of-band, \eg from 
their smartphones.
More precisely, they exchange metadata on \(f\), encryption keys, and
some of
\changeAL{routing information that they will use to transfer the
  file's content over \name's network of unreliable nodes.} Namely,
the recipient provides a \emph{rendezvous point} for the sender to
initiate the file transfer.
\sonja{here comes more of a solution overview and reference to the outline
  figure.}

Figure \cref{fig:outline} shows the components needed to obtain this
routing information.  
%use-once reply mix-headers.
%They use these reply headers to transfer the file contents of \(f\) over a network of unreliable nodes while also achieving privacy.

@@

This rest of this section presents the different parts of the system in detail.
We align the presentation of the system with the taxonomy of 
\textcite{RoutingSurveyAnonymousProtocols}.
They classify anonymous communication protocols using the following 
categories (see~\cite[Table 1]{RoutingSurveyAnonymousProtocols}):
\begin{description}
  \item[Network structure]
    describes the characteristics of the \changeAL{network nodes}, the connections 
    between them and the underlying topology.
    The subcategories are
    \begin{enumerate*}
      \item network topology,
      \item connection type (direction, synchronization),
      \item symmetry (node roles, node topology for routing, decentralization);
    \end{enumerate*}

>>>>

Our goal is to enable private and reliable file exchange between users 
participating in the system, by using their respective devices only.
When Alice and Bob, two users of our system, want to exchange a file \(f\) 
through \name, they start by sharing some information out-of-band, \eg from 
their smartphones.
More precisely, they exchange metadata on \(f\), encryption keys, and
some use-once reply mix-headers.
They use these reply headers to transfer the file contents of \(f\) over a 
network of unreliable nodes while also achieving privacy.

\sonja{Here comes more of a solution overview and reference to the outline
  figure.}
Figure \cref{fig:outline} shows the components needed to obtain this
routing information.

@@

This rest of this section presents the different parts of the system in detail.
We align the presentation of the system with the taxonomy of 
\textcite{RoutingSurveyAnonymousProtocols}.
They classify anonymous communication protocols using the following 
categories (see~\cite[Table 1]{RoutingSurveyAnonymousProtocols}):
\begin{description}
  \item[Network structure]
    describes the characteristics of the network nodes, the connections between 
    them and the underlying topology.
    The subcategories are
    \begin{enumerate*}
      \item network topology,
      \item connection type (direction, synchronization),
      \item symmetry (node roles, node topology for routing, decentralization);
    \end{enumerate*}
